---
title: "case study"
author: Yiyao LI
output: github_document
---

```{r setup}
library(tidyverse)
library(p8105.datasets)
library(leaflet)
data(nyc_airbnb)
```

## Brainstorm some questions

1. What's the best Airbnb in staten island for< $100
2. What price range is popular in each borough? most rented?
3. What apartment features are related to price?
4. cheapest room type in each neighborhood?
5. hosts have higher ratings?



## Answer the questions

clean the data
convert the scores to the stars

```{r}
nyc_airbnb =
  nyc_airbnb %>%
  mutate(stars = review_scores_location/2)
```

group by the neighbourhood group and room type 

```{r}
nyc_airbnb %>%
  count(neighbourhood_group, room_type) %>% 
  pivot_wider(names_from = room_type, values_from = n)
```

get some information about the relationship between price and the features of the rooms.

```{r}
nyc_airbnb %>%
  group_by(neighbourhood_group, room_type) %>% 
  summarize(mean_price = mean(price))
```

find the romm price difference in Manhattan's different neighbourhoods.

```{r}
nyc_airbnb %>%
  filter(neighbourhood_group == "Manhattan") %>% 
  count(neighbourhood)
  
nyc_airbnb %>%
  filter(
    price < 1000,
    neighbourhood_group == "Manhattan") %>% 
  mutate(neighbourhood = fct_reorder(neighbourhood, price)) %>% 
  ggplot(aes(x = neighbourhood, y = price)) +
    geom_boxplot()+
    coord_flip()
```

```{r}
nyc_airbnb %>% 
  sample_n(1000) %>% 
  ggplot(aes(x = lat, y = long, color = price)) +
  geom_point()
```

```{r}
pal <- colorNumeric("viridis", nyc_airbnb %>% pull(stars))

nyc_airbnb %>% 
  sample_n(5000) %>% 
  leaflet()
  addProviderTiles(providers$CartoDB.Position) %>%
  addCircleMarkers(~lat, ~long, radius = 1, color =~ pal(stars))
```

